### 2021-07-21 doc/thesis/chapters/hls.tex
hls intro

The main sources of information for this chapter are found in \cite{VivadoUgHLS}, TODO.

@@

@@

easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

>>>>

This chapter talks about High-Level Synthesis in general, but also specifically describes the details of the Xilinx HLS.
The main sources of information for this chapter are found in \cite{VivadoUgHLSIntro}and \cite{VivadoUgHLS}.

@@

In software development, engineers are used to writing code in a high-level language, such as C or \cplusplus.
With these languages, specific hardware details are abstracted and thus, very little knowledge of the target hardware is required.
The compiler takes over these details as it transforms the code by using the underlying, supported instruction set of the target hardware.
This has been the standard for many years by now.
In the earlier times however, it was common practise to develop programs in the low-level assembly language.
The supported instruction set of the target CPU had to be implemented directly by the software engineer.\\

A direct comparison can be drawn to FPGA design.
An FPGA engineer historically develops code in the register-transfer level (RTL), which is common practise until today.
This can be compared to developing software in the assembly language.
However, the recent development towards automation and code generation brought up High-Level Synthesis (HLS).
There, the FPGA design can be described in a high-level language, such as C or \cplusplus, which is convenient and allows to focus on the algorithm, rather than hardware details.
This high-level code is then transformed into the low-level RTL automatically, by the HLS tool.\\

The usage of HLS tries to bring software- and hardware development closer together and tries to make these two worlds more similar.
In software development, there are different compilers for multiple processor architectures, which can be used to port a program to another target hardware.
The idea of HLS is to create the same level of abstraction - write code in a high-level language, which is agnostic of its target hardware architecture.

@@

easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV.
However, it may be less optimized.
A developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.
